Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-08 doc/slides/hong+eisner.TLT13.slides.tex
added a note
put in a table
small changes
slides so far. example sentence updated (and sent to jason)

\begin{document}
\title{Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses}
\author{Juneki Hong, Jason Eisner}
\date{\today}
\frame{\titlepage}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
  \end{itemize}
}

@@

Encoded Constraints:
\begin{itemize}
  \item Connectedness
  \item Acyclicity
  \item Consistency of Directionalized Links
\end{itemize}

\NoteJH{Take from the paper.}
}

@@

\frame{\frametitle{Data Sets}
\begin{itemize}
  \item[] 18,577 English sentences with 10,960 connected parses
  \item[] 18,577 unlabeled Russian sentences with 4,913 connected parses
\end{itemize}

\frame{\frametitle{On the English data set}
\begin{itemize}
\item[] Link Data has 8\% additional edges over the CoNLL.
\item[] 52\% of links match CoNLL arcs
\item[] 57\% of CoNLL arcs match links
\end{itemize}

@@

\frame{\frametitle{ILP Results}
  \begin{itemize}
    \item[] Link types that allowed both directions:
      \begin{itemize}
        \item[] $\frac{7}{113} = 6.19\%$ 
      \end{itemize}
    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        \item[] $\frac{4043}{195000} = 2.07\%$ 
      \end{itemize}
  \end{itemize}
  \begin{itemize}
  \item[]  
  \end{itemize}
}

\frame{\frametitle{ILP Results}
  \begin{itemize}
    \item[] Link types that allowed both directions:
      \begin{itemize}
        \item[] $\frac{7}{113} = 6.19\%$ 
      \end{itemize}
    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        \item[] $\frac{4043}{195000} = 2.07\%$ 
      \end{itemize}
  \end{itemize}
  \begin{itemize}
  \item[] The link labels mostly have a consistent direction.
  \end{itemize}
}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above]{3}{\small ROOT}
	\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge above]{3}{4}{\small ADV}
	\depedge[edge above]{3}{5}{\small ADV}
	\depedge[edge below]{3}{6}{I}
	\depedge[edge above]{3}{6}{\small VC}
	\depedge[edge above, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below]{2}{1}{D}
	\depedge[edge above]{2}{1}{\small NMOD}
	\depedge[edge below]{7}{8}{MV}
    \depedge[edge above]{7}{8}{\small ADV}
	\depedge[edge below]{6}{7}{P}
	\depedge[edge above]{6}{7}{\small VC}
	\depedge[edge below]{8}{9}{J}
	\depedge[edge above]{8}{9}{\small PMOD}
	\deproot[edge below]{2}{W}
    \deproot[edge below]{7}{WV}
	\deproot[edge below]{10}{X}
	\depedge[edge below]{6}{4}{E}
	\depedge[edge below]{6}{5}{E}
  \end{dependency}
\end{figure}

\begin{itemize}
\item This is due to an inconsistency of the Link Grammar, discovered by our method. \NoteJH{The reason why is in footnote 6 of page 10 in our paper. Reread after sleeping.}
\end{itemize}

>>>>

\begin{document}
\title{Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses}
\author{Juneki Hong, Jason Eisner}
\date{\today}
\frame{\titlepage \NoteJH{Include pictures of us?}}

\section{Motivation}
\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item[]  
    \item[]  
    \item[]  
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item[]  
    \item[]  
  \end{itemize}
}

\frame{\frametitle{Motivation}
  \begin{itemize}
    \item A multiheaded dependency corpus would be useful for testing new parsing algorithms
    \item Such a corpus could be automatically annotated using Integer Linear Programming
    \item We explored whether the Link Grammar could be adapted for this purpose.
    \item[]  
  \end{itemize}
}

@@

Encoded Constraints:
\begin{itemize}
  \item Connectedness
  \item Acyclicity
  \item Consistency of Directionalized Links
\end{itemize}
}

@@

\frame{\frametitle{Data Sets}
%\begin{itemize}
%  \item[] 18,577 English sentences with 10,960 connected parses
%  \item[] 18,577 unlabeled Russian sentences with 4,913 connected parses
%\end{itemize}
  \begin{table}[h]
    \begin{tabular}{|l|l|l|}
      \hline
      & \# Sentences & \# Connected Parses \\ \hline
      English             & 18,577        & 10,960               \\ \hline
      Russian (unlabeled) & 18,577        & 4,913                \\ \hline
    \end{tabular}
  \end{table}

  On the English data set:

  \begin{itemize}
  \item[] Link Data has 8\% additional edges over the CoNLL.
  \item[] 52\% of links match CoNLL arcs
  \item[] 57\% of CoNLL arcs match links
  \end{itemize}

@@

%\frame{\frametitle{On the English data set}
%\begin{itemize}
%\item[] Link Data has 8\% additional edges over the CoNLL.
%\item[] 52\% of links match CoNLL arcs
%\item[] 57\% of CoNLL arcs match links
%\end{itemize}

%
%}

\frame{\frametitle{ILP Results}
%  \begin{table}[h]
%    \begin{tabular}{|l|l||l|}
%      \hline
%      & & out of total \\ \hline
%      Link types & & \\allowing both directions & 7 & 113 \\ \hline
%      Link tokens & & \\requiring disallowed direction & & \\via slack & 4043 & 195,000 \\ \hline
%    \end{tabular}
%  \end{table}
  \begin{itemize}
  \item[] Link types that allowed both directions:
    \begin{itemize}
    \item[] 7 / 113 = 6.19\%
    \end{itemize}
  \item[] Link tokens that required disallowed direction via slack:
    \begin{itemize}
    \item[] 4043 / 195,000 = 2.07\%
    \end{itemize}
  \end{itemize}
  \begin{itemize}
  \item[]  
  \end{itemize}
}

\frame{\frametitle{ILP Results}
  \begin{itemize}
    \item[] Link types that allowed both directions:
      \begin{itemize}
      \item[] 7 / 113 = 6.19\%
      %\item[] $\frac{7}{113} = 6.19\%$ 
      \end{itemize}
    \item[] Link tokens that required disallowed direction via slack:
      \begin{itemize}
        %\item[] $\frac{4043}{195000} = 2.07\%$ 
        \item[] 4043 / 195,000 = 2.07\%
      \end{itemize}
  \end{itemize}
  \begin{itemize}
  \item[] The link labels mostly have a consistent direction.
  \end{itemize}
}

@@

\frame{\frametitle{Link Results: Subject-Verb links are backwards}
\begin{figure}
  \begin{dependency}
	\begin{deptext}
	  {\scriptsize DT} \& {\scriptsize NN} \& {\scriptsize MD} \& {\scriptsize RB} \& {\scriptsize RB} \& {\scriptsize VB} \& {\scriptsize VB} \& {\scriptsize IN} \& {\scriptsize NN} \& {\scriptsize .} \\
	  the \& matter \& may \& never \& even \& be \& tried \& in \& court \& . \\
	  - \& n-u \& v \& e \& e \& v \& v-d \& r \& n-u \& - \\
	\end{deptext}
	\deproot[edge above, edge style = {gray}, hide label]{3}{\small ROOT}
	\depedge[edge below, edge style = {red, ultra thick}]{2}{3}{S}
	\depedge[edge above, edge style = {blue, ultra thick}]{3}{2}{\small SBJ}
	\depedge[edge above, edge style = {gray}, hide label]{3}{4}{\small ADV}
	\depedge[edge above, edge style = {gray}, hide label]{3}{5}{\small ADV}
	\depedge[edge below, edge style = {gray}, hide label]{3}{6}{I}
	\depedge[edge above, edge style = {gray}, hide label]{3}{6}{\small VC}
	\depedge[edge above, , edge style = {gray}, hide label, edge unit distance =1.5ex]{3}{10}{\small P}
	\depedge[edge below, edge style = {gray}, hide label]{2}{1}{D}
	\depedge[edge above, edge style = {gray}, hide label]{2}{1}{\small NMOD}
	\depedge[edge below, edge style = {gray}, hide label]{7}{8}{MV}
    \depedge[edge above, edge style = {gray}, hide label]{7}{8}{\small ADV}
	\depedge[edge below, edge style = {gray}, hide label]{6}{7}{P}
	\depedge[edge above, edge style = {gray}, hide label]{6}{7}{\small VC}
	\depedge[edge below, edge style = {gray}, hide label]{8}{9}{J}
	\depedge[edge above, edge style = {gray}, hide label]{8}{9}{\small PMOD}
	\deproot[edge below, edge style = {gray}, hide label]{2}{W}
    \deproot[edge below, edge style = {gray}, hide label]{7}{WV}
	\deproot[edge below, edge style = {gray}, hide label]{10}{X}
	\depedge[edge below, edge style = {gray}, hide label]{6}{4}{E}
	\depedge[edge below, edge style = {gray}, hide label]{6}{5}{E}
  \end{dependency}
\end{figure}

\begin{itemize}
\item This is due to an inconsistency of the Link Grammar, discovered by our method. 
\end{itemize}
